Comparing MTurk and the US Population's Occupational Diversity

### 2018-09-17 Manuscript.Rmd
Replication Demographic Analaysis- Age, Gender, and Ethinicity

###Replication Demographic Analaysis
#Age Analysis T- Test
#Load Dataset
require(dplyr)
require(readxl)
BLS_age <- read_excel("age_demo.xlsx")

@@

#Run t test.
t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
View(t_value)

##Gender Analysis
BLS_data <- read_excel("employment_demo.xlsx")

@@

#Sum chi-square values.
sum(gender_ch2$chi2, na.rm=TRUE)

#Ethnicity Analysis 
#Define obs_eth
BLS_cauc <- as.numeric(BLS_data[7, 4])/100
BLS_AfAm <- as.numeric(BLS_data[7,5])/100
BLS_Asn <- as.numeric(BLS_data[7,6])/100
BLS_Hisp <- as.numeric(BLS_data[7,7])/100
BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_Hisp)

@@

#Sum chi-square values.
sum(eth_ch2$chi2, na.rm=TRUE)

>>>>

##Replication Demographic Analaysis
##Age Analysis
```{r}
#Age Analysis T- Test
#Load Dataset
require(dplyr)
require(readxl)
BLS_age <- read_excel("age_demo.xlsx")

@@

#Run t test.
t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
View(t_value)
```

##Gender Analysis
```{r}
##Gender Analysis
BLS_data <- read_excel("employment_demo.xlsx")

@@

#Sum chi-square values.
sum(gender_ch2$chi2, na.rm=TRUE)
```

##Ethnicity Analysis
```{r}
#Ethnicity Analysis 
#Define obs_eth
BLS_cauc <- as.numeric(BLS_data[7, 4])/100
BLS_AfAm <- as.numeric(BLS_data[7,5])/100
BLS_Asn <- as.numeric(BLS_data[7,6])/100
BLS_Hisp <- as.numeric(BLS_data[7,7])/100
BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_Hisp)

@@

#Sum chi-square values.
sum(eth_ch2$chi2, na.rm=TRUE)
```
